### 2023-03-27 pv_evaluation/templates/inventor/2-summary.qmd
update
Prepare release

from er_evaluation.summary import (
    homonimy_rate,
    name_variation_rate,
)
from er_evaluation.plots import (
    compare_plots, 
    plot_cluster_sizes_distribution,
    plot_entropy_curve,
)
from pv_evaluation.benchmark import (
    inventor_benchmark_plot,
    inventor_estimates_plot,
    plot_entropy_curves,
    top_inventors,
    plot_cluster_sizes,
    plot_homonimy_rates,
    plot_name_variation_rates,
)
```

@@

display(HTML(top_inventors(disambiguations["{{ filename }}"], full_names)))
```

@@

:::{.column-body-outset}
```{python}
plot_homonimy_rates(disambiguations, full_names)
```
:::

>>>>

from er_evaluation.summary import (
    homonymy_rate,
    name_variation_rate,
)
from er_evaluation.plots import (
    compare_plots, 
    plot_cluster_sizes_distribution,
    plot_entropy_curve,
)
from pv_evaluation.benchmark import (
    inventor_benchmark_plot,
    inventor_estimates_plot,
    plot_entropy_curves,
    top_inventors,
    plot_cluster_sizes,
    plot_homonymy_rates,
    plot_name_variation_rates,
)
```

@@

display(HTML(top_inventors(disambiguations["{{ filename }}"], full_names).to_html()))
```

@@

:::{.column-body-outset}
```{python}
plot_homonymy_rates(disambiguations, full_names)
```
:::
